Evaluating Covid-19 Short-Term Forecasts using \pkg{scoringutils} in \proglang{R}

### 2021-12-12 article-knitr.Rnw
update paper and plots

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
  engine='R', 
  tidy=TRUE, 
  fig.path='plots/plot-', 
  message = FALSE, 
  warning = FALSE
)
@

@@

%% - \Abstract{} almost as usual
\Abstract{
  Forecasts play an important role in a variety of fields. Their role in informing public policy has attracted increased attention from the general public with the emergence of the Covid-19 pandemic. Much theoretical work has been done on the development of proper scoring rules and other scoring metrics that can help evaluate these forecasts. Making these theoretical insights available to end users, however, has been less of a focus. In this paper we introduce \pkg{scoringutils}, an \proglang{R} package that facilitates automated forecast evaluation. It gives the user access to a wide range of scoring metrics for various types of forecasts as well as a variety of ways to visualise the evaluation. We give an overview of the evaluation process and the metrics implemented in \pkg{scoringutils} and show a full evaluation of a set of short-term forecasts of public health related targets made by SPI-M during the 2020 Covid-19 epidemic in the United Kingdom. 
}

@@

\subsection{Proper scoring rules for non-sample-based forecasts (WIS and BS)}
For forecasts in an interval or quantile format, \pkg{scoringutils} offers the weighted interval score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. 
% properties of the WIS + decomposition
The WIS has very similar properties to the CRPS and can be thought of as a quantile-based approximation. For an increasing number of equally-spaced prediction intervals the WIS converges to the CRPS. One additional benefit of the WIS is that it can easily be decomposed into three additive components: an uncertainty penalty (sharpness) for the width of a prediction interval and penalties for over- and underprediction (if a value falls outside of a prediction interval). This can be very helpful in diagnosing model problems. It may even be useful to convert samples into quantiles and use the WIS instead of the CRPS to make use of this decomposition for the purpose of model diagnostics. 
% Brier Score
Binary forecasts can be scored using the Brier score (BS) [CITATION], which corresponds to the squared difference between the given probability and the outcome (either 0 or 1).

@@

The following section shows an example evaluation of short-term predictions of four different Covid-19 related targets in the UK made between March 31 and July 13 2020. Forecasts were produced by six research groups in the UK, and submitted to the Scientific Pandemic Influenza Group on Modelling (SPI-M). The forecasts aimed to assess the likely future burden the UK healthcare system would face from the Covid-19 pandemic. Predictions submitted to SPI-M were aggregated and used to inform UK government health policy through the Strategic Advisory Group of Experts (SAGE). All predictions as well as most of the observed values are now publicly available and discussed in more depth in [FUNK ET AL]. 
% - timing (weekly?) and number of forecast dates
% - the four targets
% - the models.

@@

\subsection{Preparing and visualising the data}

We first need to obtain the data by installing and loading the \pkg{covid19.forecasts.uk} using the following commands: 
% 
<<load-data>>=
# install and load data pacakge from external repository
# remotes::install_github("sbfnk/covid19.forecasts.uk")

# load packages
library(covid19.forecasts.uk)
library(dplyr)
library(scoringutils)

# load truth data
data(covid_uk_data)
# head(covid_uk_data)

# load forecasts
data(uk_forecasts)
# head(uk_forecasts)
@
% 
Let us take a first look a the data:
% 
<<glimpse-data>>=
glimpse(covid_uk_data)
glimpse(uk_forecasts)
@
% 
Some minor changes need to be made to the data before we can evaluate the forecasts. The names of the columns that hold the forecasts and the true observed values need to be changed to \code{prediction} and \code{true_value}. While we could also proceed with separate data sets for the evaluation, we merge the two data sets in order to remove all instances where the forecasts, but not the true observations were made public. The \pkg{scoringutils} package provides a function that attempts to merge the data sets in a sensible way. 
% 
<<modify-data>>=
uk_forecasts <- rename(uk_forecasts, prediction = value)
covid_uk_data <-rename(covid_uk_data, true_value = value)

combined <- merge_pred_and_obs(uk_forecasts, covid_uk_data)
@
% 
It is helpful to start the evaluation process by visualising the available data, as missing forecasts can impact the evaluation if missingness is not random, but instead correlates with performance. The function \fct{show\_avail\_forecasts} returns a heatmap with the number of available forecasts. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts. 
% 
\begin{figure}[h]
\centering
<<show-availability, echo=TRUE, fig.height=6.7, fig.width=12, eval = TRUE>>=
show_avail_forecasts(data = combined, 
                     x = "creation_date", 
                     show_numbers = FALSE,
                     legend_position = "bottom",
                     facet_formula = ~ value_desc)
@
\caption{\label{fig:avail-forecasts} Overview of the number of available forecasts}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
The forecasts and observed values themselves can be visualised using the \fct{plot\_predictions} function. Data visualisation is of course highly context-dependent, but the function tries to accommodate most practical use-cases. In addition to basic plotting functionality it offers the user an optional ad hoc way to filter both forecasts and observed values. This makes it possible to tweak the plot in a beginner-friendly way without having to manipulate the data separately. Forecasts and observed values can be passed in separately (and are merged internally) or as a single data.frame. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To display, for example, death forecasts from the SIRCOVID model made on the 22nd July 2020 for the four UK countries and add three weeks of prior observations to the plot, we can call: % 
\begin{figure}[h!]
\centering
<<show-forecasts, echo=TRUE, fig.height=5.2, fig.width=7, eval = FALSE>>=
locations <- 'c("Scotland", "Wales", "Northern Ireland", "England")'
plot_predictions(truth = covid_uk_data,
                 forecasts = uk_forecasts,
                 filter_both = list(paste("geography %in%", locations, collapse = ""), 
                                    'value_type == "death_inc_line"'),
                 filter_truth = list('value_date <= "2020-06-22"',
                                     'value_date > "2020-06-01"'), 
                 filter_forecasts = list('model == "SIRCOVID"', 
                                         'creation_date == "2020-06-22"'),
                 x = "value_date",
                 facet_formula = ~ geography) + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:forecast-visualisation} Short-term forecasts for incident deaths made by the SIRCOVID model on June 22 2020.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

The actual scoring of forecasts based on observed values can be performed using the function \fct{eval\_forecasts}. The function automatically detects the forecast type and format, applies the appropriate scoring metrics and aggregates results as desired by the user. Internally, operations are handled using \pkg{data.table} to allow for fast and efficient computation. The function requires a \code{data.frame} or similar with some pre-specified columns (e.g. a column called "prediction", one called "true\_value" and more depending on the forecast format). Additional columns may be present to indicate a grouping of forecasts, for example forecasts made in different locations or over different forecast horizons. To illustrate the requirements, \pkg{scoringutils} provides example data for all possible forecast formats. It also offers functions to to transform between various formats, e.g. from a sample based format to a quantile format.

When conducting an evaluation, we need to decide on the level of grouping over which we want to aggregate scores. For the UK short-term forecasts it makes sense to look at the scores achieved by every model separate for all prediction targets. This can be achieved by calling
% ion G
<<scoring, eval = TRUE>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model", "value_desc"))

glimpse(scores)
@
% 
\fct{eval\_forecasts} aggregates scores by taking the mean over according to the grouping specified in \code{summarise_by}. In the above example, if \code{summarise_by = c("model", "value_type")}, then scores would be averaged over all creation dates, forecast horizons (as represented by the the value dates), locations and quantiles to yield one score per model and forecast target. For a more detailed analysis we could for example specifiy \code{summarise_by = c("mode", "value_type", "geography")} to additionally stratify by location. If we wanted to have one score per quantile or one per prediction interval range, we could use something like \code{summarise_by = c("model", "quantile", "range")}. This would allow us to examine interval or quantile coverage or makes it possible to analyse the accuracy of the tails of the forecasts. In addition to the mean, we can also obtain the standard deviation of the scores over which we average, as well as any desired quantile, by specifying \code{sd = TRUE} and for example \code{quantiles = c(0.5)} for the median.

The user must, however, exercise some caution when aggregating scores. As explained above, many of the metrics are absolute and scale with the magnitude of the quantity to forecast. This makes it sometimes ill-advised to average over them. In the given example, looking at one score per model (i.e. specifying \code{summarise_by = c("model")}) is problematic, as overall aggregate scores would be dominated by hospital admissions, while errors on death forecasts would have little influence. Similarly, aggregating over different forecast horizons is often not a good idea as the mean will be dominated by further ahead forecast horizons.

The second important argument of the \fct{eval\_forecasts} function is the \code{by} argument that denotes the unit of a single forecast. In the above example, the unit of a single forecast would be \code{by = c("model", "geography", "value_type", "creation_date", "value_date", "value_desc")} as there is one distinct forecast for each combination of these categories. Quantiles do not need to be included, as several quantiles make up one forecast (and similarly for samples). By default, if \code{by = NULL}, \fct{eval\_forecasts} will automatically use all present columns to determine the unit of a single forecast. In the above example, we did not have to explicitly specify the \code{by} argument, as all available columns were relevant to the unit of a single forecast. If there are additional columns that do not correspond to the unit of a single forecast, like for example the observed temperature in a given location, \code{by} must be specified and these columns must be excluded.

@@

@@

<<pairwise-comparison, eval = TRUE>>=
# unsummarised scores
unsummarised_scores <- eval_forecasts(combined)
pairwise <- pairwise_comparison(unsummarised_scores, 
                                summarise_by = "value_desc")
@

@@

@@

\begin{figure}[h]
\centering
<<score-table, echo=TRUE, fig.height=7.2, fig.width=15, eval = TRUE>>=
score_table(scores, y = "model", facet_formula = ~ value_desc)
@
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<pairwise-plot, echo=TRUE, fig.height=7.2, fig.width=14, eval = TRUE>>=
plot_pairwise_comparison(pairwise) +
  ggplot2::facet_wrap(~ value_desc, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

@@

\begin{figure}[h!]
\centering
<<WIS-components, echo=TRUE, fig.height=5.2, fig.width=12, eval = TRUE>>=
wis_components(scores, 
               facet_formula = ~ value_desc, 
               scales = "free_x", 
               relative_contributions = TRUE, 
               x_text_angle = 0) + 
  ggplot2::coord_flip() + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

\begin{figure}[h!]
\centering
<<coverage, echo=TRUE, fig.height=5.2, fig.width=14, out.width="40%", fig.show='hold', eval = TRUE>>=
cov_scores <- eval_forecasts(combined, 
                             summarise_by = c("model", 
                                              "range", "quantile"))
scoringutils::interval_coverage(cov_scores)
scoringutils::quantile_coverage(cov_scores)
@

@@

% \begin{figure}[h]
% \centering
% <<
% pit-plots, echo=TRUE, fig=TRUE, height=5.2, width=12>>=
% # out <- eval_forecasts(combined, 
% #                       summarise_by = c("model"), 
% #                       pit_plots = TRUE)
% 
% @
% \caption{\label{fig:calibration-pit} pit plots}
% \end{figure}

@@

\begin{figure}[h]
\centering
<<calibration, echo=TRUE, fig.height=5.2, fig.width=15, eval = TRUE>>=
scores <- eval_forecasts(combined, 
                         summarise_by = c("model",
                                          "value_desc", 
                                          "geography"), 
                         compute_relative_skill = FALSE)
scoringutils::score_heatmap(scores, metric = "bias", 
                            x = "geography", facet_formula = ~ value_desc, 
                            scale = "free_x")
@
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}

>>>>

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
  engine='R', 
  cache=TRUE,
  tidy=TRUE, 
  tidy.opts=list(width.cutoff=60),
  fig.path='plots/plot-', 
  message = FALSE, 
  warning = FALSE, 
  prompt = TRUE,
  continue = "+  ", 
  width = 70, 
  useFancyQuotes = FALSE
)
@

@@

%% - \Abstract{} almost as usual
\Abstract{
  Forecasts play an important role in a variety of fields. Their role in informing public policy has attracted increased attention from the general public with the emergence of the Covid-19 pandemic. Much theoretical work has been done on the development of proper scoring rules and other scoring metrics that can help evaluate these forecasts. Making these theoretical insights available to end users, however, has been less of a focus. In this paper we introduce \pkg{scoringutils}, an \proglang{R} package that facilitates automated forecast evaluation. It gives the user access to a wide range of scoring metrics for various types of forecasts as well as a variety of ways to visualise the evaluation. We give an overview of the evaluation process and the metrics implemented in \pkg{scoringutils} and show an example evaluation of forecasts for COVID-19 cases and deaths submitted to the European Forecast Hub between May und September 2021. 
}

@@

\subsection{Proper scoring rules for non-sample-based forecasts (WIS and BS)}
For forecasts in an interval or quantile format, \pkg{scoringutils} offers the weighted interval score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. 
% properties of the WIS + decomposition
The WIS has very similar properties to the CRPS and can be thought of as a quantile-based approximation. For an increasing number of equally-spaced prediction intervals the WIS converges to the CRPS. One additional benefit of the WIS is that it can easily be decomposed into three additive components: an uncertainty penalty (called dispersion or sharpness) for the width of a prediction interval and penalties for over- and underprediction (if a value falls outside of a prediction interval). This can be very helpful in diagnosing model problems. It may even be useful to convert samples into quantiles and use the WIS instead of the CRPS to make use of this decomposition for the purpose of model diagnostics.

% Brier Score
Binary forecasts can be scored using the Brier score (BS) [CITATION], which corresponds to the squared difference between the given probability and the outcome (either 0 or 1).

@@

% The following section shows an example evaluation of short-term predictions of four different Covid-19 related targets in the UK made between March 31 and July 13 2020. Forecasts were produced by six research groups in the UK, and submitted to the Scientific Pandemic Influenza Group on Modelling (SPI-M). The forecasts aimed to assess the likely future burden the UK healthcare system would face from the Covid-19 pandemic. Predictions submitted to SPI-M were aggregated and used to inform UK government health policy through the Strategic Advisory Group of Experts (SAGE). All predictions as well as most of the observed values are now publicly available and discussed in more depth in [FUNK ET AL]. 
% - timing (weekly?) and number of forecast dates
% - the four targets
% - the models.

The following section shows an example evaluation of short-term predictions for COVID-19 cases and deaths submitted to the European Forecast Hub [CITATION]. The full oficial hub evaluations, which also use \pkg{scoringutils}, can be seen at https://covid19forecasthub.eu/. The European Forecast Hub each week collates, aggregates and evaluates one to four week ahead predictions of different COVID-19 related targets submitted by different research groups. Forecasts are submitted in a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The following example evaluation is based on a subset of forecasts from the European Forecast Hub which includes one to three week ahead forecasts made between May and September 2021 for COVID-19 cases and deaths from four different models.

This example data follows a quantile-based format, but the evaluation process would work analogously for forecasts in a different format. We will point out differences to scoring different forecast formats where appropriate. The example data set (as well as versions of it in different formats) is also included in the \pkg{scoringutils} package.

@@

\subsection{Checking the data}

% 
<<load-data>>=
# load packages
library(scoringutils)
library(dplyr)
library(data.table)
library(kableExtra)

# load forecasts
data(example_quantile)
@
% 
All higher level functions that allow for convenient evaluation of forecasts expect a \code{data.frame} or similar. Lower-level functions (discussed in a later section) accept inputs as vectors and matrices.

We omit \code{NA} values as the data set also contains entries for which we have an observed value, but no forecast. 
% 
<<glimpse-data>>=
example_quantile |>
  na.omit() |>
  glimpse()
@
%

For forecasts in a quantile-based format it is necessary to have columns called \code{true_value}, \code{prediction} and \code{quantile}. It is recommended (although not necessary except in order to do pairwise comparisons) to have a column called "model" with an identifier for the forecaster.
Table \ref{tab:column-requirements} shows the columns expected for different input formats.

<<column-requirements>>=
requirements <- 
  data.table(
    "Format" = c("quantile-based", "sample-based", "binary", "pairwise-comparisons"), 
    `Required columns` = c("'true_value', 'prediction', 'quantile'", 
                           "'true_value', 'prediction', 'sample'", 
                           "'true_value', 'prediction'", 
                           "additionally a column 'model'")
  )

requirements |>
  kable(format = "latex")
@

We can check whether the data conforms to the requirements by running \fct{check\_forecasts}.

<<>>=
check_forecasts(example_quantile)
@

This returns a list with different entries giving information about what \pkg{scoringutils} infers from the data. \code{target_type} \code{prediction_type} refer to the forecast format. \code{forecast_unit} contains a vector of the columns which \pkg{scoringutils} thinks denote the unit of a single forecast. This means that in this instance a single forecast (with a set of 23 quantiles) can uniquely be identified by the values in the columns "location", "target\_end\_date", "target\_type", "location\_name", "forecast\_date", "model", "horizon". In this example, having "location" as well as "location\_name" included does not make a difference, as they contain duplicated information. In general, however, it is strongly advised to remove all unnecessary columns that do not help identify a single forecast. \code{unique_values} gives an overview of the number of unique values per column across the entire data set, providing a first hint as to whether the forecast set is complete. \code{warnings} shows potential warnings about the data. In this example, \pkg{scoringutils} warns that there are observed values present for which there is no corresponding forecast. These warnings can often be ignored, but may provide important information. If there are errors that cannot be ignored, a list entry \code{errors} will appear.

It is helpful to start the evaluation process by visualising data availability, as missing forecasts can impact the evaluation if missingness is not random, but instead correlates with performance. The function \fct{show\_avail\_forecasts} returns a heatmap with the number of available forecasts. By default, the function treats a set of different quantiles or samples as one forecast. However, the user can specify manually which elements to treat as one forecast and which categories to sum over to count the number of available forecasts. 
% 
\begin{figure}[h]
\centering
<<show-availability, echo=TRUE, fig.height=6.7, fig.width=12, eval = TRUE>>=
show_avail_forecasts(data = example_quantile, 
                     x = "target_end_date", 
                     show_numbers = FALSE,
                     legend_position = "bottom",
                     facet_formula = ~ target_type)
@
\caption{\label{fig:avail-forecasts} Overview of the number of available forecasts}
\end{figure}
%THINK ABOUT WHETHER THIS FUNCTION CAN BE COMBINED WITH THE OTHER HEATMAP FUNCTION. 
% 
The forecasts and observed values themselves can be visualised using the \fct{plot\_predictions} function. Data visualisation is of course highly context-dependent, but the function tries to accommodate most practical use-cases. In addition to basic plotting functionality it offers the user an optional ad hoc way to filter both forecasts and observed values. This makes it possible to tweak the plot in a beginner-friendly way without having to manipulate the data separately. Forecasts and observed values can be passed in separately (and are merged internally) or as a single data.frame. Conditions to filter on need to be provided as a list of strings, where each of the strings represents an expression that can be evaluated to filter the data. To display, for example, short-term forecasts for COVID-19 cases and deaths made by the EuroCOVIDhub-ensemble model on June 28 2021 as well as 5 weeks of prior data, we can call: % 
\begin{figure}[h!]
\centering
<<show-forecasts, echo=TRUE, fig.height=5.2, fig.width=7, eval = TRUE>>=
plot_predictions(data = example_quantile,
                 x = "target_end_date",
                 filter_truth = list('target_end_date <= "2021-07-15"',
                                     'target_end_date > "2021-05-22"'),
                 filter_forecasts = list("model == 'EuroCOVIDhub-ensemble'",
                                         'forecast_date == "2021-06-28"'),
                 facet_formula =  target_type ~ location, 
                 ncol = 4) + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:forecast-visualisation} Short-term forecasts for COVID-19 cases and deaths made by the EuroCOVIDhub-ensemble model on June 28 2021.}
\end{figure}
% 
The output is shown in Figure \ref{fig:forecast-visualisation}.

@@

The actual scoring of forecasts based on observed values can be performed using the function \fct{eval\_forecasts}. The function automatically detects the forecast type and format (as shown in the output of \fct{check\_forecasts}), applies the appropriate scoring metrics and can in addition also aggregate results as well as perform pairwise comparisons between models. Internally, operations are handled using \pkg{data.table} to allow for fast and efficient computation.

<<>>=
scores <- eval_forecasts(example_quantile)
glimpse(scores)
@

The above produces one score for every forecast. However, we usually like to summarise scores to learn about average performance.

We can either run a separate function to summarise the scores, 
<<>>=
summarised_scores <- 
  summarise_scores(scores = scores, 
                   summarise_by = c("model", "target_type"))
@

or we score and summarise in one function call:

<<>>=
summarised_scores <- 
  eval_forecasts(example_quantile, 
                 summarise_by = c("model", "target_type"))
@

<<>>=
summarised_scores
@

% 
\fct{eval\_forecasts} and \fct{summarise\_scores} aggregate scores by taking the mean over according to the grouping specified in \code{summarise_by}. In the above example, if \code{summarise_by = c("model", "target_type")}, then scores would be averaged over all other categories to obtain one score per model and forecast target type. For a more detailed analysis we could for example specify \code{summarise_by = c("mode", "target_type", "location")} to additionally stratify by country. Summarised scores can be visualised using the function \fct{scores\_table} as is shown in Figure \ref{fig:score-table}.

If we wanted to have one score per quantile or one per prediction interval range, we could use something like \code{summarise_by = c("model", "quantile", "range")}. This would allow us to examine interval or quantile coverage or makes it possible to analyse the accuracy of the tails of the forecasts. In addition to the mean, we can also obtain the standard deviation of the scores over which we average, as well as any desired quantile, by specifying \code{sd = TRUE} and for example \code{quantiles = c(0.5)} for the median.

The user must, however, exercise some caution when aggregating scores. As explained above, many of the metrics are absolute and scale with the magnitude of the quantity to forecast. This makes it sometimes ill-advised to average over them. In the given example, looking at one score per model (i.e. specifying \code{summarise_by = c("model")}) is problematic, as overall aggregate scores would be dominated by case forecasts, while errors on death forecasts would have little influence. Similarly, aggregating over different forecast horizons is often not a good idea as the mean will be dominated by further ahead forecast horizons.

\begin{figure}[h]
\centering
<<score-table, echo=TRUE, fig.height=7.2, fig.width=15, eval = TRUE>>=
score_table(summarised_scores, y = "model", facet_formula = ~ target_type)
@
\caption{\label{fig:score-table} Coloured table to visualise the computed scores}
\end{figure}

@@

Again there are two possible ways to do pairwise comparisons. First, the function \fct{pairiwse\_comparison} can be called to compare models against each other. Here \code{summarise_by} denotes what relative skill scores shall be computed for. \code{summarise_by = "model"} means there will be one relative skill score per model, while \code{summarise_by = c("target_type", "target_type")} would mean there is one relative skill score per model, computed completely separately for different target types.

When using \fct{pairwise\_comparison}, it is important that the scores used as input have not been summarised in any way.

<<>>=
pairwise <- pairwise_comparison(scores, 
                                baseline = "EuroCOVIDhub-baseline")

pairwise2 <- pairwise_comparison(scores, 
                                summarise_by = c("model", "target_type"), 
                                baseline = "EuroCOVIDhub-baseline")
@

@@

@@

\begin{figure}[h!]
\centering
<<pairwise-plot, echo=TRUE, fig.height=7.2, fig.width=14, eval = TRUE>>=
plot_pairwise_comparison(pairwise2) +
  ggplot2::facet_wrap(~ target_type, scales = "free_x") 
@
\caption{\label{fig:pairwise-comparison} Ratios of mean scores based on overlapping forecast sets. If a tile is blue, then the model on the y-axis performed better. If it is red, the model on the x-axis performed better in direct comparison. }
\end{figure}

@@

@@

@@

\begin{figure}[h!]
\centering
<<WIS-components, echo=TRUE, fig.height=5.2, fig.width=12, eval = TRUE>>=
wis_components(summarised_scores, 
               facet_formula = ~ target_type, 
               scales = "free_x", 
               relative_contributions = TRUE, 
               x_text_angle = 0) + 
  ggplot2::coord_flip() + 
  ggplot2::theme(legend.position = "bottom")
@
\caption{\label{fig:wis-components} p-values and ratios together.}
\end{figure}

@@

<<pit-plots, echo=TRUE, fig.height=5.2, fig.width=14, out.width="49%", fig.show='hold', eval = TRUE>>=
pit <- pit_df(example_quantile, 
              summarise_by = "model", "target")

hist_PIT(pit)
@

\begin{figure}[h!]
\centering
<<coverage, echo=TRUE, fig.height=5.2, fig.width=14, fig.show='hold', eval = TRUE>>=
cov_scores <- eval_forecasts(example_quantile, 
                             summarise_by = c("model", "target_type",
                                              "range", "quantile"))

scoringutils::interval_coverage(cov_scores, facet_formula = ~ target_type)
@

<<quantile-coverage, fig.height=5.2, fig.width=14, fig.show='hold', eval = TRUE>>=
scoringutils::quantile_coverage(cov_scores, facet_formula = ~ target_type)
@

@@

% \begin{figure}[h]
% \centering
% <<
% pit-plots, echo=TRUE, fig=TRUE, height=5.2, width=12>>=
% # out <- eval_forecasts(example_quantile, 
% #                       summarise_by = c("model"), 
% #                       pit_plots = TRUE)
% 
% @
% \caption{\label{fig:calibration-pit} pit plots}
% \end{figure}

@@

\begin{figure}[h]
\centering
<<calibration, echo=TRUE, fig.height=5.2, fig.width=15, eval = TRUE>>=
scores <- eval_forecasts(example_quantile, 
                         summarise_by = c("model",
                                          "target_type", 
                                          "location_name"), 
                         compute_relative_skill = FALSE)
scoringutils::score_heatmap(scores, metric = "interval_score", 
                            x = "location_name", facet_formula = ~ target_type, 
                            scale = "free_x")
@
\caption{\label{fig:bias-heatmap} bias by location}
\end{figure}
